### 2018-09-09 ANA-TOPQ-2017-07-PAPER-metadata.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.0}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
These are the most restrictive direct bounds on $tqH$ interactions measured so far.
}

>>>>

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.0}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, are exploited in the two analyses respectively. 
Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
These are the most restrictive direct bounds on $tqH$ interactions measured so far.
}

### 2018-09-09 sections/conclusion.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

>>>>

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

### 2018-09-09 sections/data_presel.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirements.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton triggering the event.  
Furthermore, at least four jets are required, of which at least two must be $b$-tagged.

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected charged light lepton is required to match, with $\Delta R < 0.15$, the lepton triggering the event and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Charged light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and trailing $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

%Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
%with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
%For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
%For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
%along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
%with looser identification criteria and no isolation requirements.
Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.  
Furthermore, at least four jets are required, of which at least two must be $b$-tagged.

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected electron or muon is required to match, with $\Delta R < 0.15$, the lepton reconstructed by the trigger 
and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected electrons or muons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
               & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and trailing $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2018-09-09 sections/detector.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification information for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a
steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The muon spectrometer measures the %deflection
trajectories
of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking 
chambers located in a toroidal field of approximately 0.5~T and 1~T in the central and endcap regions, respectively. 
The muon spectrometer is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 
a software-based High-Level Trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

>>>>

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification information for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the end-caps. 
The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 
a software-based High-Level Trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-09-09 sections/introduction.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of $\ttbar$ events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. 
Searches targeting signatures with two same-charge light leptons (electrons or muons) or three charged light leptons, generically referred to as ``multileptons",
are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton signatures resulting from 
$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}.

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.

>>>>

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. 
Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons",
are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton signatures resulting from 
$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}.

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes.
Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.
